### 2012-10-01 inst/examples/multiple_uncertainty.Rmd
attempting multiple uncertainties using matrix approach -- Example on growth-noise alone

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
#options(device = function(width = 5, height = 5) {
#    pdf(NULL, width = width, height = height)
#})
````

@@

``` {r }
xmin <- 0
xmax <- 150
grid_n <- 100
````

@@

With purely growth noise, a row of the matrix is given by the probability density of the growth noise with mean $f(x,h)$, that is, the probability of tranistion from $x$ to $x_{t+1}$ at harvest $h$ is given by the function $P(x_t+1, f(x,h))$ for some probability density function $P$.  In the case of uncertainty in stock $y$ and harvest $h$, we must integrate over the probability distributions for possible harvests and possible stock sizes,

<div> $$ \int dh \int dy P(x_{t+1}, f(y, h))P(y)P(h) $$</div>

In general this convolution can be non-trivial to compute, but in the case of uniformly distributed harvest error of $\pm \sigma_i$ around some quota $q$, and uniform measurement error of $\pm \sigma_m$ around the true stock size $x$, the integrals can be written as,

<div> $$ \frac{1}{(q+\sigma_i) - \max(q-\sigma_i,0)} \frac{1}{(x+\sigma_m) - \max(x-\sigma_m,0)} \int_{\max(q-\sigma_i,0)}^{q+\sigma_i} dh \int_{\max(y-\sigma_h,0)}^{y+\sigma_h} dy P(x_{t+1}, f(y, h)) $$ </div>

Note we enforce the simple non-negative boundary on stock and harvest.

So now we are left to merely integrate the $f(y,h)$ over these finite intervals.  We can do this for arbitrary $f$ through multidimensional numerical integration (In fact we could have done this in the first place, but it is too slow for the convolutions of arbitrary probability densities)

```{r}
int_f
```

If we assume a simple function like logistic growth, \\(f(s) = r s (1-s/K) + s \\), where \\(s = x - h\\),

@@

Following Sethi et al, we can do this in closed form,

```r
F
```

We can compare timing and equivalence of these two expressions:

```{r }
require(cubature)
# Confirm that these give the same value, and time performance
system.time(a <- sapply(x_grid, function(x) int_f(f, x, 1, .1, .1, pars)))
system.time(b <- sapply(x_grid, function(x) F(x, 1, .1, .1, pars)))
ggplot(data.frame(x=x_grid,a=a,b=b)) + geom_line(aes(x,a), col="red") + geom_line(aes(x,b), lty=2)
```

Note that as the uncertainy gets small, we recover the original transition probability $f$:

```{r }
F(50, 4, .1, .1, pars)
F(50, 4, .0001, .0001, pars)
f(50,4,pars)
```

When the noise width is much smaller than the bin width we may have trouble, particularly with the uniform distribution, since part of the bin corresponds to zero density, part to high density.

@@

We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .1
sigma_m <- .5
sigma_i <- .5
````

@@

```{r }
pdfn <- function(P, s) dunif(P, 1 - s, 1 + s)
#pdfn <- function(P, s) dlnorm(P, 0, s)
```

@@

```{r }
sdp <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=sigma_g, pdfn, sigma_m=sigma_m, sigma_i=sigma_i, F)
```

```{r }
uniform <- find_dp_optim(sdp, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
```

Do the deterministic exactly,

```{r deterministic}

SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = sigma_g, pdfn)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

Determine the policies for each of the scenarios (noise combinations).

```{r eval=FALSE, include=FALSE}
  z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_i

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
```

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
#policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1], mc=opt$D[,1]), id = "stock")
policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1]), id = "stock")

ggplot(policy) + geom_jitter(aes(stock, stock-x_grid[value], color=variable), shape="+")
dat <- subset(policy, stock < 140)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```

>>>>

``` {r  echo=FALSE, cache=FALSE }
#opts_knit$set(upload.fun = socialR::flickr.url)
#options(device = function(width = 5, height = 5) 
#                   pdf(NULL, width = width, height = height))
````

@@

``` {r }
xmin <- 0
xmax <- 150
grid_n <- 20
````

@@

With purely growth noise, a row of the matrix is given by the probability density of the growth noise with mean $f(x,h)$, that is, the probability of tranistion from $x$ to $x_{t+1}$ at harvest $h$ is given by the function $P(x_t+1, f(x,h))$ for some probability density function $P$.

We assume a simple function like logistic growth, \\(f(s) = r s (1-s/K) + s \\), where \\(s = x - h\\),

@@

@@

We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  $\Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x}$, conditioned on $h > x$ and $x > 0$

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .1
sigma_m <- 0
sigma_i <- 0
````

@@

```{r }
pdfn=function(P, mu, s){
                          if(mu==0)
                            if(P == 0)
                              1
                            else 
                              0
                          else 
                          dunif(P,mu*(1-s),mu*(1+s))
}

ln <- function(P, mu, s) dlnorm(P, log(mu), s)
```

@@

```{r }
sdp <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, sigma_g, pdfn, sigma_m, sigma_i)
```

```{r }
mult <- find_dp_optim(sdp, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
```

Compare to the former method:

```{r deterministic}
pdfn_old <- function(P,s) dunif(P, 1-s, 1+s)
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = sigma_g, pdfn_old)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)

policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], new = mult$D[,1]), id = "stock")
ggplot(subset(policy, stock < 120)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable), shape="+")

dat <- subset(policy, stock < 120)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,120, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```
